---
title: "Shopify_DS_Challenge"
output: html_document
---

```{r}
library(tidyverse)
library(dlookr)
```


```{r}
library(readxl)
X2019_Winter_Data_Science_Intern_Challenge_Data_Set <- read_excel("C:/Users/shaun/Downloads/2019 Winter Data Science Intern Challenge Data Set.xlsx")
shopShoes <- X2019_Winter_Data_Science_Intern_Challenge_Data_Set
```

```{r}
describe(shopShoes)
```

```{r}
summary(shopShoes)
```
We will look only at order_amount and total_items as they are fields which contain numerical values which we can analyse.

For the order_amount column, we can see that the 3rd quartile value is quite close to the median but the maximum (or the last value)
is substantially faraway from the median. This gives us strong hints of it being an outlier.

For the total_items column, we again see that the 3rd quartile value is quite close to the median but the maximum (or the last value)
is substantially faraway from the median. For this scenario as well, we see strong hints of it being an outlier.

We can see that in those two columns, there might be outliers that are skewing our mean values.

```{r}
diagnose_outlier(shopShoes)
```

We can see that both the columns under investigation contain a very small number of outliers, when taken in context with the size of the dataset i.e. 141 and 18 for order_amount and total_items respectively.

```{r}
shopShoes_cols <- shopShoes %>% dplyr::select(order_amount, total_items)
plot_outlier(shopShoes_cols)
```

Looking at the y-axes in the graphs for both the columns, we see that having outliers in the dataset values makes a lot
of difference, skewing the graphs to a great extent.


```{r}
boxplot(shopShoes_cols)
```

We will attempt to remove the rows that are outliers. In this process, we will first start by taking values
for total_items in our dataset that are less than 2000, as we a few rows with the value 2000, followed by a
massive drop with a value of 8.

Also for order_amount, we will drop values that are less than 704000, as we a few rows with the value 704000
which is very high as compared to the median. We will keep iterating on this column till we have very few outliers.

```{r}
shopShoes_cleaned1 <- shopShoes_cols[shopShoes_cols$total_items < 2000, ]

shopShoes_cleaned1 <- shopShoes_cols[shopShoes_cols$order_amount < 704000, ]
```

```{r}
diagnose_outlier(shopShoes_cleaned1)
```


Iterating on the order_amount column with a maximum threshold of 100000, dropped from 704000.

```{r}
shopShoes_cleaned2 <- shopShoes_cols[shopShoes_cols$order_amount < 100000, ]
diagnose_outlier(shopShoes_cleaned2)
```


Iterating on the order_amount column with a maximum threshold of 50000, dropped from 100000.

```{r}
shopShoes_cleaned3 <- shopShoes_cols[shopShoes_cols$order_amount < 50000, ]
diagnose_outlier(shopShoes_cleaned3)
```


Iterating on the order_amount column with a maximum threshold of 25000, dropped from 50000.

```{r}
shopShoes_cleaned4 <- shopShoes_cols[shopShoes_cols$order_amount < 25000, ]
diagnose_outlier(shopShoes_cleaned4)
```


Iterating on the order_amount column with a maximum threshold of 715, dropped from 25000.
(Arrived on the value 715 after trial and error using the diagnose_outlier function, where I was
attempting to see which threshold limit would give me a respectably least amount of outliers.)

```{r}
shopShoes_cleaned5 <- shopShoes_cols[shopShoes_cols$order_amount < 715, ]
diagnose_outlier(shopShoes_cleaned5)
```


```{r}
summary(shopShoes_cleaned5)
```

Q1a. 
What went wrong with our calculation was that our dataset contained outliers that were skewing our metrics.
To evaluate the data better, we could remove the outliers and then look at the descriptive statistics for the dataset.
The alternative would be to look at the median.

Q1b.
We can look at the descriptive statistics for the cleaned dataset, specifically the average order value (AOV).
Or we could just look at the median from the original datset as it is not as affected as the mean, by the outliers.

Q1c.
By removing the outliers, we now have a mean value (average order value (AOV)) that might better represent the 
data. This new value of mean we obtain is 293.3.
We also have a median of 280 for the cleaned dataset.

If we decide to look at the original dataset, we would have a median of 284.
Looking at both the median values and comparing it to the mean we obtained, we can say that the 
average order value (AOV) for the cleaned dataset would represent the dataset quite well.



